---
title: "Macro B - PS 3"
author: "Doron Zamir"
date: "5/18/2021"
output:
  html_document: default
  pdf_document: 
    fig_caption: yes
    highlight: haddock
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  eval = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)
```

# Getting things ready

## Load Packages

```{r load_pack}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse,
  readxl,
  DataExplorer,
  lpirfs,
  tinytex
)
```

## Load Data

```{r}
data_raw <- read_xlsx("PS3_Data.xlsx") %>% 
  drop_na
```

## Split the Data

Splitting the data into different data sets:

### Endogenous Data

```{r}
data_endog <- data_raw %>% select(
  ln_f,
  u,
  n,
  ln_LF,
  ln_CPI,
  ln_RW
)
```

### The Instrument

```{r}
data_iv <- data_raw %>% select(
  eMP
)
```

### Shock Data

```{r}
data_shock <- data_raw %>% select(
  FFR
)
```

### Controls / Exogenous Data

```{r}
exog_data <- data_raw %>% select(
  ln_f,
  ln_CPI,
  R1,
  MN2,
  ln_markup,
  SW1,
  SW2,
  SW3,
  SW4
)
```

### Contemporary Data

```{r}
contemp_data <- data_raw %>% select(
  t,
  t2,
  t3,
  t4
)
```

## Impulse Response Function

### Computing a 95% confidence interval:

```{r}
irf_95 <- lp_lin_iv(
  endog_data = data_endog,
  shock = data_shock,
  use_twosls = TRUE,
  instrum = data_iv,
  lags_endog_lin = 0,
  exog_data = exog_data,
  lags_exog = 2,
  contemp_data = contemp_data,
  lags_criterion = NaN,
  max_lags = NaN,
  trend = 0,
  confint =1.645,
  use_nw = TRUE,
  nw_lag = NULL,
  nw_prewhite = FALSE,
  adjust_se = FALSE,
  hor = 12
)
```

### Computing a 68% confidence interval:

```{r}
irf_68 <- lp_lin_iv(
  endog_data = data_endog,
  shock = data_shock,
  use_twosls = TRUE,
  instrum = data_iv,
  lags_endog_lin = 0,
  exog_data = exog_data,
  lags_exog = 2,
  contemp_data = contemp_data,
  lags_criterion = NaN,
  max_lags = NaN,
  trend = 0,
  confint =c(1,1.645),
  use_nw = TRUE,
  nw_lag = NULL,
  nw_prewhite = FALSE,
  adjust_se = FALSE,
  hor = 12
)
```

## Plotting

### 95% confident interval

```{r}
plot_lin(irf_95)
```

### 68% confident interval

```{r}
plot_lin(irf_68)
```

## Analysis

### 

| Variable     | Model                                                                          | Data                                                                                              |
|--------------|--------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------|
| GDP / Output | drops down sharply at t = 0, and than converges back to the baseline in t = 7  | drops down at t = 2, and neve goes back to baseline                                               |
| Unemployment | spikes up sharply at t = 2, and than slowly converges to the baseline in t = 7 | rises up slowly in t = 0 to t =5, and than seems to be steady at a higher level then the baseline |
| Employment   | Drops down with Output                                                         | Drops down with Output                                                                            |
| Labor Force  | Drops down with Output (but not as much as output)                             | Drops down slower than output                                                                     |
| Inflation    | Drop down immediately, converges fast back to baseline                         | the same                                                                                          |
| Real Wages   | Drop down immediately, converges slowly back to baseline                       | drops down and not coming back                                                                    |

```{}
```
